### 2013-09-25 intro.tex
add archive preprint to exact learning paper reference
align logo slightly differently, add stuff to future work.
some graphics, minor fixes.

%\includegraphics[width=\linewidth]{python_soul}%
%\flushright%
%Randall Munroe, \emph{xkcd.com}
\end{minipage}%
\\[2cm]
In computer vision research, the goal is to automatically extract information
from a given image or image sequence.  In particular discerning semantic
information, that is interpreting an image, is a prominent research topic.
While much progress has been made in recent years, computer vision systems still lag behind
human vision in most tasks that require semantic information. These tasks can often be formulated
in terms of \emph{semantic classes}, meaning categories of parts, objects or scenes.
Examples include answering questions such as ``Is this a picture of a beach?'', ``How many
cars are there in this image?'' or even ``What objects lie on the table?''.
These questions illustrate a range of possible tasks involving semantic categories,
such as classifying images of single objects, localization and counting of object classes,
and parsing a scene fully into objects and object classes together with their relations.
%
While humans can distinguish tens of thousands of object classes, and have
little trouble in interpreting complex scenes, current methods are often
restricted to a much smaller number of classes and only have limited
capabilities to model interactions or relations.  We believe that
\emph{context} is one of the most important cues when it comes to classifying
objects, and therefore understanding scenes. Therefore, we target dense
labeling of scenes, taking object relations into account.  The task of densely
labeling image pixels into classes is called object class segmentation or
semantic segmentation.
\pagebreak

@@

In the following we distinguish between the task of semantic segmentation,
which usually distinguishes unstructured ``stuff'' classes such as road and
grass, and object class segmentation, which denotes the segmentation of very
structured classes, such as cars, planes and people. We consider four
different datasets in this thesis: the object class segmentation datasets
Graz-02~\citep{marszatek2007accurate} and Pascal VOC 2010~\citep{pascal}, and the semantic segmentation datasets
MSRC-21~\citep{shotton2006textonboost} and NYU V2~\citep{SilbermanECCV12}.
%
Both tasks have the same ultimate goal of parsing, and therefore understanding,
images in terms of semantic classes. However they employ different mechanisms
to represent and process.

@@

@@

Finally, Chapter~\ref{ch:nyu} applies the methods developed in
Chapter~\ref{ch:structured_pystruct} and Chapter~\ref{ch:exact_learning} to the
problem of semantic annotation with structure classes in RGB-D data. We
demonstrate that we are able to learn meaningful spatial relations, and outperform
state-of-the-art methods on the NYU V2 datasets.
\pagebreak

\section{Publications}
The main material of this thesis has either been published in conference
proceedings or has been submitted to conferences or journals. We now list the
relevant publications.
\begin{description}
    \item[Chapter~\ref{ch:itm}]%
        \emph{Information Theoretic Clustering using Minimum Spanning Trees}\\
        Andreas C. M\"uller, Sebastian Nowozin and Christoph H. Lampert.
        Published in the proceedings of the German Conference on Pattern
        Recognition.
    \item[Chapter~\ref{ch:semi_supervised}]%
        \emph{Multi-Instance Methods for Partially Supervised Image
        Segmentation}\\
        Andreas C. M\"uller and Sven Behnke. Published in the proceedings of
        the IARP Workshop on Partially Supervised Learning.
    \item[Chapter~\ref{ch:structured_pystruct}]%
        \emph{PyStruct - Structured Prediction in Python}\\
        Andreas C. M\"uller and Sven Behnke. Submitted to the Journal of
        Machine Learning Research, Open Source Software track.
    \item[Chapter~\ref{ch:exact_learning}]%
        \emph{Learning a Loopy Model for Semantic Segmentation Exactly}\\
        Andreas C. M\"uller and Sven Behnke.  Submitted to the International
        Conference on Computer Vision Theory and Applications.
    \item[Chapter~\ref{ch:nyu}]%
        \emph{Learning Depth-Sensitive Conditional Random Fields for Semantic Segmentation}\\
        Andreas C. M\"uller and Sven Behnke. Submitted to the International
        Conference on Robotics and Automation.
\end{description}

>>>>

%\includegraphics[width=\linewidth]{python_soul}%
%\flushright%
%Randall Munroe, \emph{xkcd.com}
\end{minipage}%
\\[2cm]
In computer vision research, the goal is to automatically extract information
from a given image or image sequence.  In particular discerning semantic
information, that is interpreting an image, is a prominent research topic.
While much progress has been made in recent years, computer vision systems still lag behind
human vision in most tasks that require semantic information. These tasks can often be formulated
in terms of \emph{semantic classes}, meaning categories of parts, objects or scenes.
Examples include answering questions such as ``Is this a picture of a beach?'', ``How many
cars are there in this image?'' or even ``What objects lie on the table?''.
These questions illustrate a range of possible tasks involving semantic categories,
such as classifying images of single objects, localization and counting of object classes,
and parsing a scene fully into objects and object classes together with their relations.
%
While humans can distinguish tens of thousands of object classes, and have
little trouble in interpreting complex scenes, current methods are often
restricted to a much smaller number of classes and only have limited
capabilities to model interactions or relations.  We believe that
\emph{context} is one of the most important cues when it comes to classifying
objects, and therefore understanding scenes. Therefore, we target dense
labeling of scenes, taking object relations into account.  The task of densely
labeling image pixels into classes is called object class segmentation or
semantic segmentation.\pagebreak\\

@@

In the following we distinguish between the task of semantic segmentation,
which usually distinguishes unstructured ``stuff'' classes such as road and
grass, and object class segmentation, which denotes the segmentation of very
structured classes, such as cars, planes and people. We consider four
different datasets in this thesis: the object class segmentation datasets
Graz-02~\citep{marszatek2007accurate} and Pascal VOC 2010~\citep{pascal}, and
the semantic segmentation datasets MSRC-21~\citep{shotton2006textonboost} and
NYU V2~\citep{SilbermanECCV12}. Examples can be found in \Figref{pascal_msrc}.
%
Both tasks have the same ultimate goal of parsing, and therefore understanding,
images in terms of semantic classes. However they employ different mechanisms
to represent and process.

@@

\begin{figure}[t]
    \begin{center}
    \begin{tabu} to 0.8\linewidth{@{}XX@{}}
    \includegraphics[width=\linewidth]{msrc_scene}&%
    \includegraphics[width=\linewidth]{msrc_scene_GT}\\
    \includegraphics[width=\linewidth]{pascal}&%
    \includegraphics[width=\linewidth]{pascal_gt}
    \end{tabu}
    \end{center}
\caption{%
    Examples from the MSRC-21 (top) and Pascal VOC (bottom) datasets with
    ground-truth annotation. MSRC-21 contains mostly texture classes, such as
    tree, building, street and sky, but also objects, like cars in this example.
    Pascal VOC contains only object classes, such as person, cat, table and
    bottle, and an additional background class (black).
\figlabel{pascal_msrc}}
\end{figure}

@@

Finally, Chapter~\ref{ch:nyu} applies the methods developed in
Chapter~\ref{ch:structured_pystruct} and Chapter~\ref{ch:exact_learning} to the
problem of semantic annotation with structure classes in RGB-D data. We
demonstrate that we are able to learn meaningful spatial relations, and outperform
state-of-the-art methods on the NYU V2 datasets.

\section{Publications}
The main material of this thesis has either been published in conference
proceedings or has been submitted to conferences or journals. We now list the
relevant publications.
\begin{description}
    \item[Chapter~\ref{ch:itm}]%
        \emph{Information Theoretic Clustering using Minimum Spanning Trees}\\
        Andreas C. M\"uller, Sebastian Nowozin and Christoph H. Lampert.
        Published in the proceedings of the German Conference on Pattern
        Recognition.
    \item[Chapter~\ref{ch:semi_supervised}]%
        \emph{Multi-Instance Methods for Partially Supervised Image
        Segmentation}\\
        Andreas C. M\"uller and Sven Behnke. Published in the proceedings of
        the IARP Workshop on Partially Supervised Learning.
    \item[Chapter~\ref{ch:structured_pystruct}]%
        \emph{PyStruct - Structured Prediction in Python}\\
        Andreas C. M\"uller and Sven Behnke. Submitted to the Journal of
        Machine Learning Research, Open Source Software track.
    \item[Chapter~\ref{ch:exact_learning}]%
        \emph{Learning a Loopy Model for Semantic Segmentation Exactly}\\
        Andreas C. M\"uller and Sven Behnke.\ arXiv preprint 1309.4061, Submitted to the International
        Conference on Computer Vision Theory and Applications.
    \item[Chapter~\ref{ch:nyu}]%
        \emph{Learning Depth-Sensitive Conditional Random Fields for Semantic Segmentation}\\
        Andreas C. M\"uller and Sven Behnke. Submitted to the International
        Conference on Robotics and Automation.
\end{description}

### 2013-09-25 structured_prediction/paper.tex
some graphics, minor fixes.

\section{CRFs for Semantic Segmentation}\seclabel{semantic_segmentation}
Structured models based on factor graphs, as described in \Secref{factor_graphs} are often
referred to as Conditional Random Fields (CRFs), pointing to their
probabilistic interpretation.
Conditional Random Fields have been established as an important tool in many
areas of computer vision. Applications include dense stereo, optical flow, 
inpainting, de-noising, image editing, low-level segmentation and semantic segmentation.

@@

Using superpixels instead of pixels has large computational advantages.  A
model that uses superpixels contains much fewer variables than one that works
on pixel-level.  Typical sizes for superpixels are in the hundereds of pixels,
leading to a hundred-fold decrease in the number of variables. There are also
semantic advantages. Using superpixels can constitute a form of regularization,
including prior knowledge about the structure of images. Modeling interactions
between superpixels also allows more distant parts of an image to interact,
instead of modeling long-term relations only indirectly over neighbors.
Finally, modeling decisions on a superpixel-level allows for more context for a
local decision, while semantic decisions on pixel-level are not meaningful near
object boundaries.  The main disadvantage of superpixel-based approaches is
that the initial oversegmentation can not be influenced by later reasoning.
This can be a problem if fine structures need to be segmented for which local
evidence does not suffice.

@@

%TODO where does that leave us now?
In Chapter~\ref{exact_learning} and Chapter~\ref{nyu}, we investigate
superpixel-based conditional random fields learned with conditional random
fields. Our emphasis is on understanding the learning, and how to cope with the
complexity of inference in loopy models.

>>>>

\section{CRFs for Semantic Segmentation}\seclabel{semantic_segmentation}
%
Structured models based on factor graphs, as described in \Secref{factor_graphs} are often
referred to as Conditional Random Fields (CRFs), pointing to their
probabilistic interpretation.
Conditional Random Fields have been established as an important tool in many
areas of computer vision. Applications include dense stereo, optical flow, 
inpainting, de-noising, image editing, low-level segmentation and semantic segmentation.

@@

Using superpixels instead of pixels has large computational advantages.  A
model that uses superpixels contains much fewer variables than one that works
on pixel-level.  Typical sizes for superpixels are in the hundereds of pixels,
leading to a hundred-fold decrease in the number of variables. There are also
semantic advantages. Using superpixels can constitute a form of regularization,
including prior knowledge about the structure of images. Modeling interactions
between superpixels also allows more distant parts of an image to interact,
instead of modeling long-term relations only indirectly over neighbors.
Finally, modeling decisions on a superpixel-level allows for more context for a
local decision, while semantic decisions on pixel-level are not meaningful near
object boundaries.  The main disadvantage of superpixel-based approaches is
that the initial oversegmentation can not be influenced by later reasoning.
This can be a problem if fine structures need to be segmented for which local
evidence does not suffice.
%
\begin{figure}
    \begin{tabu} to \linewidth{@{}XX@{}}
    \includegraphics[width=\linewidth]{structured_prediction/images/scene_sp_org}&%
    \includegraphics[width=\linewidth]{structured_prediction/images/scene_sp}\\
    \includegraphics[width=\linewidth]{structured_prediction/images/scene_sp_graph}&%
    \includegraphics[width=\linewidth]{structured_prediction/images/scene_sp_gt}
\end{tabu}
\caption{%
    Schematic of CRFs over superpixels. From left to right: input image, superpixel segmentation
    using SLIC into about 100 superpixels, pairwise potential in the CRF, and desired labeling.
\figlabel{superpixel_illustration}}
\end{figure}

@@

%TODO where does that leave us now?
In Chapter~\ref{ch:exact_learning} and Chapter~\ref{ch:nyu}, we investigate
superpixel-based conditional random fields learned using structural support
vector machines. The emphasis of Chapter~\ref{ch:exact_learning} is on
understanding the learning, and how to cope with the complexity of inference in
loopy models, while Chapter~\ref{ch:nyu} extends the approach to RGB-D images
and shows how we can learn spatial relations using parametric pairwise
potentials.
